Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

Although any of the existing triplet sampling strategies, such as Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance}, and the within-batch Hardest negative
sampling method, can be selected for source and destination hardness,
not all combinations are effective and efficient.
%
In this subsection, we find a proper combination empirically.

@@

As HM is expected to increase the hardness of the source triplet, we first sort
the triplet sampling methods according to their approximated mean hardness of
$1000$ mini-batches from CUB dataset with an imagenet-initialized RN18 model,
as shown in~\cref{tab:hsort}.

In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest, as shown in \cref{tab:hsort}.

>>>>

Although any of the existing triplet sampling strategies, such as Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance}, and the within-batch Hardest negative
sampling method, can be selected for source hardness $H_\mathsf{S}$ and
destination hardness $H_\mathsf{D}$, not all combinations are effective and
efficient.
%
In this subsection, we find a proper combination empirically as a baseline for
further experiments.

@@

As HM is expected to increase the hardness of the source triplet, we first sort
the triplet sampling methods according to their approximated mean hardness of
$1000$ mini-batches from CUB dataset with an imagenet-initialized RN18 model,
as shown in~\cref{tab:hsort}.
%
Then we adversarially train models on the CUB dataset with all possible
combinations, and summarize their R@1 and ERS performance in \cref{tab:desth}.
